Shift-sensitive Power Transformations for Transforming Data to Normality

### 2023-04-06 manuscript/manuscript.Rmd
Added configuration parameters.

First we draw $m_d=10000$ random asymmetric generalised normal distributions, parametrised as above. As before, for each distribution, up to $10 \%$ of instances are replaced by outlier values, and this is repeated $10$ times. We then compute residuals after optimising robust shift-sensitive transformations with the empirical tapered cosine weighting method.

>>>>

First we draw $m_d=10000$ random asymmetric generalised normal distributions. As before, each distribution is parametrised with a randomly chosen skewness parameter $\alpha \sim U\left(0.01, 0.99\right)$ and shape parameter $\beta \sim U\left(1.00, 5.00 \right)$. Location and scale parameters are set as $\mu = 0$ and $\sigma = 1$, respectively. $n = \lceil 10^\gamma \rceil$ values are then randomly drawn, with $\gamma \sim U\left(1.47, 3.00\right)$, which leads to between $30$ and $1000$ values being drawn to create $\mathbf{X}_i$. As before, for each distribution, up to $10 \%$ of instances are replaced by outlier values, and this is repeated $10$ times. We then compute residuals after optimising robust shift-sensitive transformations with the empirical tapered cosine weighting method.
